Analysis of the inference of ratings and rankings on Higher Order Networks with complex topologies

### 2025-09-05 draft/draft.tex
progress

>>>>

The boundary and coboundary operators and their duals can be used to define the so called Hodge Laplacians
$$
\mathcal{L} = (\partial + \partial^*)^2 = \partial \partial^* + \partial^* \partial
: C\to C
$$
and
$$
L = (d+d^*)^2 = dd^* + d^*d : C^*\to C^*
$$
where the fact that $\partial^2 = (\partial^*)^2 = 0$ and $d^2=(d^*)^2=0$ is used.
The first identity $\partial^2=0$ is implied by the alternating properties of the definition of $\partial$, from where the other identities follow.
These Hodge Laplacians satisfy the following decomposition in direct sums
$$
\mathcal{L}
=
\mathcal{L}_0
\oplus
\mathcal{L}_1
\oplus
\mathcal{L}_2
$$
and
$$
L = L_0 \oplus L_1 \oplus L_2,
$$
where in turn
$$
\mathcal{L}_k = \mathcal{L}_k^{\downarrow} \oplus \mathcal{L}_k^{\uparrow} : C_k\to C_k,
$$
$$
L_k = L_k^{\downarrow} \oplus L_k^{\uparrow} : C_k^* \to C_k^*,
$$
$$
\mathcal{L}_k^{\downarrow} = \partial_k^*\partial_k : C_k \to C_{k-1} \to C_k,
$$
$$
\mathcal{L}_k^{\uparrow} = \partial_{k+1}\partial_{k+1}^* : C_k \to C_{k+1} \to C_k,
$$
$$
L_k^{\uparrow} = d_k^*d_k : C_k^* \to C_{k+1}^* \to C_k^*,
$$
and
$$
L_k^{\downarrow} = d_{k-1}d_{k-1}^* : C_k^* \to C_{k-1}^* \to C_k^*.
$$
